MLISA: Machine Learning-based \\ Intelligent Service Agents

### 2014-11-05 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

abs

>>>>

Web services are loosely-coupled business applications willing to
cooperate in distributed settings within different groups called
communities. Communities aim to provide web services with better
visibility, efficiency, market share and total payoff. A number of
mechanisms and models have been recently proposed to aggregate web
services and make them cooperate within their communities.
However, forming optimal and stable communities as coalitions to
maximize individual and group efficiency and income is yet to be
addressed. In this paper, we propose an efficient community
formation mechanism using cooperative game-theoretic techniques,
particularly Shapley value, core, $\epsilon$-core and convex
games. We propose a mechanism for community membership requests
and selections of web services under two scenarios: (1) there is
only one community and many web services aim to join it; and (2)
web services can join different established communities. The
ultimate objective is to develop a mechanism for web services to
form stable groups allowing them to maximize their efficiency and
generate near-optimal (welfare-maximizing) communities where a
taxation-based solution is being proposed. The theoretical and
extensive experimental results show that our algorithms provide
web services and community owners, in real-world-like
environments, with applicable and near-optimal decision making
mechanisms.
